### 2019-04-03 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
pyro info

%\section{Pyrolysis}
%

\section{Carbon nano-wire}
Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand $n m$; composed mostly by carbon atoms aligned parallel to the long axis of the fiber. \cite{Nataraj2012} Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form. \cite{Nataraj2012} Carbon nano-wires are typically fabricated by electrospinning and pyrolysis/carbonization as the main processes. During the fabrication process, the polymer molecules are to be crosslinked to prevent melting during the subsequent pyrolysis. The carbonization step removes non-carbonized components in form of condensable and incondensable gases \cite{Basu2018} to then yield carbon structures of about 50\% to 75\% of the mass of the original polymeric structure \cite{Nataraj2012}.

>>>>

\section{Pyrolysis}
Pyrolysis is technique that involves heating of biomass in the absence of air or oxygen at a maximum pyrolysis temperature. A small amount of oxygen can burn the structures and make them unusable \cite{Pramanick2018}. Once the maximum pyrolysis temperature is reached, the temperature remains constant to produce solid char, liquids, and non-condensable products. In most cases the liquid product is the main interest of the pyrolysis process, and the properties of the pyrolysis products depend on the maximum pyrolysis temperature and the heating rate \cite{Pramanick2018,Basu2018}.

The heating of large biomass molecules results in decomposition. The pyrolysis decomposition process comprises char, liquids (condensable gases) and non-condensable gases; where the consensable gases may suffer further decomposition into non-condensable gases such as $C O$, $C O_{2}$, $H_{2}$, and $C H_{4}$. Equation \ref{eq:genPyrolysis} is a general representation of the pyrolysis decomposition reaction \cite{Basu2018}.

\begin{equation}
C_{n} H_{m} O_{p} (biomass) \overset{heat}{\rightarrow} \underset{liquid}{\Sigma} C_{x} H_{y} O_{z} + \underset{gas}{\Sigma} C_{a} H_{b} O_{c} + H_{2} O + C (char)
\label{eq:genPyrolysis}
\end{equation}

Pyrolysis yields solid products that are more energy dense than the initial biomass, however the gas and liquid products are less energy dense \cite{Basu2018}. The liquid product of pyrolysis is usually of colour black containing hydrocarbons with a large amount of oxygen and 20\% water. When the liguid product is of interest, a rapid "quenching`` (freeze) is required after pyrolysis to prevent further decomposition or reaction with other substances \cite{Basu2018}. The solid yields of pyrolysis is usually around 85\% carbon with some oxygen, hydrogen and other substances that are present within the initial biomass \cite{Basu2018}. The biomass decomposition by pyrolysis produces non-condensable and condensable gases. The vapors (condensable gases) add up to the liquid yield of pyrolysis which is generated upon cooling. The gases (non-condensable gases) are comprised by ethylene, ethane, methane, carbon monoxide and carbon dioxide \cite{Basu2018}.

\section{Carbon nano-wire}
Carbon nano-wires (CMWs) are known as long, thin strings with diameters between 10 and 1 thousand $n m$; composed mostly by carbon atoms aligned parallel to the long axis of the fiber \cite{Nataraj2012}. Carbon nano-wires are different from carbon nano-tubes, as CMWs are not composed by graphene sheets in cylindrical form \cite{Nataraj2012}. Carbon nano-wires are typically fabricated by electrospinning and pyrolysis/carbonization as the main processes. During the fabrication process, the polymer molecules are to be crosslinked to prevent melting during the subsequent pyrolysis. The carbonization step removes non-carbonized components in form of condensable and incondensable gases \cite{Basu2018} to then yield carbon structures of about 50\% to 75\% of the mass of the original polymeric structure \cite{Nataraj2012}.
